The ChEMBL database as Linked Open Data

### 2012-03-07 article.tex
Andra will join too, making ChEMBL literature citation counting in CitedIn

% For one author:
\author[A]{\fnms{Egon} \snm{Willighagen}\thanks{Corresponding author.\\ E-mail: egon.willighagen@maastrichtuniversity.nl.}}
% Two or more authors (order to be determined):
\author[B]{\fnms{Ola} \snm{Spjuth}},
\author[C]{\fnms{Peter} \snm{Ansell}},
\author[D]{\fnms{Antony} \snm{Williams}},
\author[D]{\fnms{Valery} \snm{Tkachenko}},
\author[E]{\fnms{Janna} \snm{Hastings}},
\author[F]{\fnms{John} \snm{Overington}},
\author[F]{\fnms{Anna} \snm{Gaulton}},

\address[A]{Department of Bioinformatics - BiGCaT, Maastricht University, ADDRESS, Maastricht,\\ The Netherlands\\
E-mail: egon.willighagen@maastrichtuniversity.nl}
\runningauthor{E.L. Willighagen et al.}
\address[B]{Uppsala University}
\address[C]{University of Queensland}
\address[D]{Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A.}
\address[E]{ChEBI, European Bioinformatics Institute}
\address[F]{ChEMBL, European Bioinformatics Institute}

@@

%\subsubsection{CitedIn}

%Andra: use the SPARQL end point to find which entries in ChEMBL cite what papers

%The link between data and formal publication is important in many areas of
%attribution, scientist ranking, etc, as outline in \cite{Waagmeester2012}.
%ChEMBL contains many literature references, and we wish to query this data
%for CitedIn.

@@

%\subsection{Use Case 2: Chem2Bio2RDF}

%David: Chem2Bio2RDF

>>>>

% For one author:
\author[A]{\fnms{Egon} \snm{Willighagen}\thanks{Corresponding author.\\ E-mail: egon.willighagen@maastrichtuniversity.nl.}}
\runningauthor{E.L. Willighagen et al.}
% Two or more authors (order to be determined):
\author[A]{\fnms{Andra} \snm{Waagmeester}}
\author[B]{\fnms{Ola} \snm{Spjuth}},
\author[C]{\fnms{Peter} \snm{Ansell}},
\author[D]{\fnms{Antony} \snm{Williams}},
\author[D]{\fnms{Valery} \snm{Tkachenko}},
\author[E]{\fnms{Janna} \snm{Hastings}},
\author[F]{\fnms{John} \snm{Overington}},
\author[F]{\fnms{Anna} \snm{Gaulton}},

\address[A]{Department of Bioinformatics - BiGCaT, Maastricht University, ADDRESS, Maastricht,\\ The Netherlands}
\address[B]{Uppsala University}
\address[C]{University of Queensland}
\address[D]{Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A.}
\address[E]{ChEBI, European Bioinformatics Institute}
\address[F]{ChEMBL, European Bioinformatics Institute}

@@

\subsubsection{CitedIn}

Andra: use the SPARQL end point to find which entries in ChEMBL cite what papers

The link between data and formal publication is important in many areas of
attribution, scientist ranking, etc, as outline in \cite{Waagmeester2012}.
ChEMBL contains many literature references, and we wish to query this data
for CitedIn.

@@
